Using VDMS to Search 100M Images: A Piece of Cake

### 2020-02-10 yfcc100m/paper/vldb2020/eval.tex
Update final plots
Update fonts on figures

To evaluate the access to metadata and images, we use the following four queries:
\begin{enumerate}
\item {\bf {\em 1tag}}: Find metadata/images of alligator.
\item {\bf {\em 1tag\_resize}}: Find metadata/images of alligator and resize to 224x224.
\item {\bf {\em 1tag\_resize\_geo}}: Find metadata/images of alligator, resize to 224x224, and in a particular geolocation (20 degrees radius).
\item {\bf {\em 2tag\_resize}}: Find metadata/images of BOTH alligator and lake and resize to 224x224.
\end{enumerate}

\begin{figure}[]
\centering
\includegraphics[width=\columnwidth]{figures/concurrency_vdms}
\caption{Concurrency Analysis - VDMS}
\label{fig:concurrency_vdms}
\end{figure}

>>>>

In order to evaluate VDMS and the baseline on certain queries, we
implement 4 queries that would enable us to retrieve certain specific images.
We choose these queries because they represent typical use-case where a
cohort of images is to be retrieve and processed from a large corpus of data.
We use the metadata associated to the images to filter said images.
In particular, this dataset contains a set of around 1500 machine generated
tags to each image.
Tags includes things like objects (chair, person, people, etc), and
concepts like places (indoor, outdoor, lake) and others (party, etc).
Together with each tag, a probability is assign.
This is, an image can have the tags people, person, party, outdoor, and each
tag will be accompanied by a probability of that tag in that image.
We represent that probability
On average there are 8 tags assigned to each image.
Also, some images have geo-location information (latitude/longitude).

We use the tags (because they contain information about the content of
the image), as well as the geo-location (as an example of searchable properties
of the images).

On top of that, we assume the use case of further processing of images
through the use of ML, such as Convolutional Neural Networks TODO-CITE HERE.
For this, we resize the images to 224x224, which is the input layer size for
a popular neural network for object detection on images: ResNet TODO-CITEHERE.

To evaluate the access to metadata and images,
we use the following four queries:
\begin{enumerate}
\item {\bf {\em 1tag}}: Find metadata/images with 1 specific tag (i.e. alligator, lake, etc).
\item {\bf {\em 1tag\_resize}}: Find metadata/images with 1 specific tag and resize to 224x224.
\item {\bf {\em 1tag\_resize\_geo}}: Find metadata/images with 1 specific tag, resize to 224x224, and in a particular geolocation (with a 20 degrees radius in latitude and longitude).
\item {\bf {\em 2tag\_resize\_geo}}: Find metadata/images with 2 specific tags (i.e. alligator AND lake) and resize to 224x224.
\end{enumerate}

It is important to note that then querying for images with certain tags, we
also apply a filter using the probability. To give an example, we only retrieve
images with a tag "alligator" and a probability higher than 92\%.
This probabilities are both present in VDMS (in the form of metadata present
in the connection between the image and that tag), as well as in MySQL (in
the form of a column of the table that links images with tags).

\begin{figure}[]
\centering
\includegraphics[width=\columnwidth]{figures/concurrency_comparison}
\caption{Concurrency Analysis on Query \"1tag\_resize\"- VDMS vs Baseline}
\label{fig:concurrency_vdms}
\end{figure}
